Fish do not need Visas: the transboundary nature of world fished species

### 2019-12-16 Manuscript_Draft.Rmd
Updates to draft

---
title: "Fish do not need Visas: the transboundary nature of world fished species"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
subtitle: "DRAFT DO NOT SHARE"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  pdf_document:
    fig_caption: yes
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
geometry: margin=1in
editor_options:
  chunk_output_type: inline
# bibliography: ./References/FishForVisa_Ref.bib
# csl: ./References/science.csl
---

@@

We estimate a total of 633 transboundary species in the world, more than double the number previously estimated [@Teh:2015gd] (Fig. 1). We also find that fisheries on these species contribute substantially to both landings and revenue. Between 2010 and 2016, fleets targeting shared stocks within EEZs landed an average of **X** tonnes, representing **X%** of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue. These values are higher than previously estimated [@Teh]. The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1).

We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts. The Asian region with a total number of **xxx** transboundary species contributing to **xx**% to the region's total landings and **xx**% of total revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz]. The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute. The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks that contribute **xx**% to total landings and **xx**% of revenue of countries along the Sea's rim. The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.

```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}

@@

![**Number of transboundary species by EEZ and their revenue by country**](./Figures/Fig1.png)

@@

```{r Status_Table, eval = T, echo = F}

@@

data.frame(Stock_Status,
           Rules) %>% 
  kable(, booktabs = T,
        caption = "Rules to determine the status of each transboundary species") %>%
  kable_styling(full_width = F) %>%
  column_spec(1,width = "3cm") %>% #wraps text in column2
  column_spec(2,width = "13cm") #%>% #wraps text in column2

>>>>

---
title: "Fish do not need Visas: the transboundary nature of world fished species"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
subtitle: "DRAFT DO NOT SHARE"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: inline
# bibliography: ./References/FishForVisa_Ref.bib
# csl: ./References/science.csl
---

@@

We estimate a total of 633 transboundary species in the world, more than double the number previously estimated [@Teh:2015gd] (Fig. 1A). We also find that fisheries on these species contribute substantially to both landings and revenue. Between 2005 and 2014, fleets targeting shared stocks within EEZs landed an average of 69 million tonnes, representing around 64% of the global catch (within EEZs), and generating USD 79.7 million in fishing revenue, equivalent to 49.8% of total revenue. These values are higher than previously estimated [@Teh]. Transboundary species are particularly important in terms of catch and revenue in regions of the world like Eastern Asia and Latin America and the Caribbean (Fig 1B). Particular in Northern America (Bermuda, Canada, Greenland, and the US), a moderate amount of catch (3.4 thousand tons) are worth 11.7 billion USD, highlighting the importance of transboundary species to the economy of the region. This is the case of the US where 116 species are responsible for up to 12.20 million USD and Peru where 28 species are responsible for USD 5.2 million (Fig 1A).

```{r Call_Map, eval = F, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="A) Number of transboundary species per EEZ and they contribution to countries fishing revenue. The number of species is represented in the EEZ while the revenue is represented in the land polygon. B) Regional revenue (left) and catch (right) contribution of tranbsoundary species."}

@@

![**A) Number of transboundary species per EEZ and they contribution to countries fishing revenue. The number of species is represented in the EEZ while the revenue is represented in the land polygon. B) Regional revenue (left) and catch (right) contribution of tranbsoundary species.**](./Figures/Fig1.png)

We found transboundary fisheries to be of substantial economic importance in regions with historic fisheries-related conflicts. The Asian region with a total number of **310** transboundary species contributing  **20'.4 million tons** to the region's total landings and **19.3 billion USD** in revenue has experienced 43.0% of all documented international fisheries conflicts since 2000 [@Spijkers:2019cz]. The European Union, Norway, Iceland, and the Faroe Islands have been at odds over the size and relative allocation of total allowable catches (TACs) for mackerel since 2007 [@Spijkers:2017ij], a species that is transboundary and contributes **xx** to landings and **xx** in revenue to the countries involved in the dispute. The Mediterranean, a region that has experienced conflicts since the 1980s [@Kliot:1989kv], is home to a large number of transboundary stocks contributing over 6 million tones worth over **8 billion USD** to countries along the Sea's rim. The identification of current transboundary species is a first step towards establishing joint management plans for marine resources [@Link:2010ei], key not only to sustain fisheries over the long term, but also to avoid international conflict.

@@

```{r Status_Table, eval = F, echo = F}

@@

data.frame(Stock_Status,
           Rules) %>% 
  kable("latex", booktabs = T,
        caption = "Rules to determine the status of each transboundary species") %>%
  kable_styling(full_width = F) %>%
  column_spec(1,width = "3cm") %>% #wraps text in column2
  column_spec(2,width = "13cm") #%>% #wraps text in column2
